\begin{problem}{MasterSpark}
{masterspark.in}{masterspark.out}
{2 seconds}{256 Megabytes}

\epigraph{Shoot through the Galaxy, Master Spark!!!}{Master Spark user}

This was a decisive battle for future of the Earth.
Invasion of the moon rabbits was inevitable and
United Command decided to use the ultimate weapon called ``Master Spark''.
It is a powerful all-annihilating beam.
The destructive beam is very big, so one can assume it has a shape
of a cylinder of radius $r$ (infinite in both front and back directions).
Master Spark went through the moon annihilating all matter on its way.
As you know, rabbits (especially moon ones) reproduce very fast.
They live on the moon surface and speed of their reproduction depends on
residental area (all moon surface). So United Command needs to know the area
of annihilated moon surface to estimate the number of enemies.
Now this is your turn to save mankind.
Calculate the destoyed area of the moon.
Remember, ``Master Spark'' is a bidirectional infinite all-annihilating beam.

\InputFile

First line of input file contains four numbers --- radius of the moon
and coordinates of its center at the time of the ``Master Spark'' shot.
Next line contains four numbers --- radius of the destructive beam and
coordinates of some point on axis of the cylinder. ``Master Spark'' was
fired from point $(0,0,0)$. All numbers are integers and do not
exceed $10^3$ by absolute value.

\OutputFile

Output the destroyed area of the moon surface.
The answer should be accurate to at least four decimal digits.

\Examples

\begin{example}
\exmp{
10 100 0 0
5 1 0 0
}{
168.357443
}%
\exmp{
10 100 0 0
50 0 1 0
}{
0.0000
}%
\end{example}

\end{problem}
